Draft-assinment1

### 2017-02-15 Draft-xuezhou-sjb.Rmd
add TOC

@@

#2. Objective

#3. Dataset Preparation
Our analysis focuses on the data of year 2012 -2013 of 23 variables. We chose the median income 6 years after graduation as our predictor variable, and eliminated many fields with bunch of missing values as well as some fields not pertainig enougn to post-graduation income. We then fosued primarily on a set of 23 variables, including gender, age, ethnic, acedemic costs, family income, completetion rates and replayment rate.

@@

| Variable Name    | Data Type         | Description                                                         | Categoriy in Documentation       |
| --------------  | ------------------ | ---------------------------------------------------------------------| --------------------------------|
| NPT4_COMBINE    | Numeric            |average net price for TITLE IV institutions of both public and private.|  Cost                       |
| DEP_STAT_PCT_IND | Numeric           |Percentage of students who are financially independent                |     Cost                        |
| PAR_ED_PCT_1STGEN| Numeric           |Percentage first-generation students                                  |      Sudent Body                |
| MD_FAMINC        | Numeric           |Median family income in real 2015 dollars                             |       Earning                   |
| PCTPELL          | Numeric           |Percentage of undergraduates who receive a Pell Grant                 |        Financial Aid            |
| PCTFLOAN         | Numeric           |Percent of all federal undergraduate students receiving a federal student loan      |  Financial Aid    |
| GRAD_DEBT_MDN    | Numeric           |The median debt for students who have completed                       |   Financial Aid                 |
| WDRAW_DEBT_MDN   | Numeric           |The median debt for sutdents who have not completed                      |Financial Aid |
| MD_EARN_WNE_P6   | Numeric           |Median income six years after entry                       |     earning   |
| MD_EARN_WNE_P10  | Numeric           |Median income ten years after entry                       |     earning  |
| RPY_3YR_RT_SUPP  | Numeric           |Repayment rate 3 years after entering repayment                       |Repayment   |
| CDR3             | Numeric           |Loan default rate 3 years afer entering repayment                       |Repayment        |
| variable$qreF    | Factor            |Predominant degree offered                      |School       |
| variable$ctrF    | Factor            |Control of institution                      |School     |
| variable$STABBR  | Factor            |State                      |School     |
| APPL_SCH_PCT_GE2 | Numeric           |Percentage of students submitting 2 or more than 2 applications                       | Student        |

@@

#4. Goals
#5. Summary of variables
##5.1 Individual variable summary

@@

#6. Relationship between variables
#6.1 NPT4_COMBINE VS State

@@

#6.2 Debt VS Cost
We assume there would be a strong linear relationship between the average net price for Title IV institutions and the median debt for students who have completed. We hypothese that the students who completed education in colleges with high costs will have a highe value of median debt. We use the following code to generate the scatterplot between these two variables to verify our assumptions.

@@

#6.3 Percentage of Pell Grant VS college type(CONTROL)

@@

#6.4  Percentage first-generation students VS Status
To compare the Percentage first-generation students with the different states, we grouped data into the state level to take a further analysis.

@@

#6.5 family income with Pell Grant
We assume there would be a strong linear relationship between family income and the percentage of students who can receive the Pell Grant. We hypothese that colleges with small value of family income would tend to have high percentages of Pell Grant. The following codes are used to generate the scatter pkot between these two varaibles.

@@

#6.6 cost and median debts with earning

@@

##6.6 default with earning

@@

##6.7 degree type vs. earning

@@

#6.7 predominant degree, control  and earning after 6 year of entry
The following plot shows two factor variables (predominant degree award variable and control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry. Our team uses the function geom_tile()[ggplot2 package] to visualize the correlation matrix.

@@

#6.8 predominant degree + control (count)
The following plot shows the relationship between two factor variables (predominant degree award variable and control variable). Our team uses the function geom_bar() to map the counting values to y, ctrF variable to x and the preF variable to the fill of the bar.

@@

Our team further uses the function xtabs() to calculate the exact number for each predominant degree awarded by different types of colleges.
```{R}
> data_clean %>%
+ xtabs(formula = ~preF+ctrF)
```

#6.9 control + earning
The following plot shows one factor variable (control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry). We use the 
geom_violin() using the default scale = “area” argument and geom_boxplot() function to explore the relationship. The plot superimposed with boxplots shows side-by-side violin plots of median earnings of students working and not enrolled 6 years after entry according to different college types.

>>>>

#Table of Contents
*1. Introduction
*2. Goal
*3. Dataset Preparation
*4. Objective
*5. Summary of variables
    *5.1 Individual variable summary
       *5.1.1 School
          *5.1.1.1 State
          *5.1.1.2 Predominant Degree
          *5.1.1.3 Control of Institution
       *5.1.2 Student Body
          *5.1.2.1 Percentage first-generation students
          *5.1.2.2 Number of applications
       *5.1.3 Cost 
          *5.1.3.1 Average net price for Title IV institutions(both public and private institutions)
          *5.1.3.2 Percentage of students who are financially independent
       *5.1.4 Financial Aid
          *5.1.4.1 Percentage of undergraduates who receive a Pell Grant
          *5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan
          *5.1.4.3 The median debt for students who have completed
          *5.1.4.4 The median debt for students who have not completed
       *5.1.5 Earning
          *5.1.5.1 Median family income in real 2015 dollars
          *5.1.5.2 Earning after graduation
       *5.1.6 Repayment
          *5.1.6.1 3-year Repayment rate
          *5.1.6.2 3-year Default rate
*6. Relationship between variables
    *6.1 NPT4_COMBINE VS State
    *6.2 Debt VS Cost
    *6.3 Percentage of Pell Grant VS college type(CONTROL)
    *6.4 Percentage first-generation students VS Statu
    *6.5 family income with Pell Grant
    *6.6 cost and median debts with earning
    *6.7 default with earning
    *6.8 degree type vs. earning
    *6.9 predominant degree, control  and earning after 6 year of entry
    *6.10 predominant degree + control (count)
    *6.11 control + earning
*7. Comparison between variables
*8. Findings and Conclusion

@@

#2. Goal
#3. Dataset Preparation
Our analysis focuses on the data of year 2012 -2013 of 23 variables. We chose the median income 6 years after graduation as our predictor variable, and eliminated many fields with bunch of missing values as well as some fields not pertainig enougn to post-graduation income. We then fosued primarily on a set of 23 variables, including gender, age, ethnic, acedemic costs, family income, completetion rates and replayment rate.

@@

| Variable Name    | Data Type         | Description                                                          |    Category in Documentation       |
| --------------  | ------------------ | ---------------------------------------------------------------------| --------------------------------|
| NPT4_COMBINE    | Numeric            |average net price for TITLE IV institutions of both public and private.|  Cost                       |
| DEP_STAT_PCT_IND | Numeric           |Percentage of students who are financially independent                |     Cost                        |
| PAR_ED_PCT_1STGEN| Numeric           |Percentage first-generation students                                  |      Sudent Body                |
| MD_FAMINC        | Numeric           |Median family income in real 2015 dollars                             |       Earning                   |
| PCTPELL          | Numeric           |Percentage of undergraduates who receive a Pell Grant                 |        Financial Aid            |
| PCTFLOAN         | Numeric           |Percent of all federal undergraduate students receiving a federal student loan      |  Financial Aid    |
| GRAD_DEBT_MDN    | Numeric           |The median debt for students who have completed                       |   Financial Aid                 |
| WDRAW_DEBT_MDN   | Numeric           |The median debt for sutdents who have not completed                   |Financial Aid |
| MD_EARN_WNE_P6   | Numeric           |Median income six years after entry                                   |     earning   |
| MD_EARN_WNE_P10  | Numeric           |Median income ten years after entry                                   |     earning  |
| RPY_3YR_RT_SUPP  | Numeric           |Repayment rate 3 years after entering repayment                       |Repayment   |
| CDR3             | Numeric           |Loan default rate 3 years afer entering repayment                     |Repayment        |
| variable$qreF    | Factor            |Predominant degree offered                                            |School       |
| variable$ctrF    | Factor            |Control of institution                                                |School     |
| variable$STABBR  | Factor            |State                                                                 |School     |
| APPL_SCH_PCT_GE2 | Numeric           |Percentage of students submitting 2 or more than 2 applications       | Student        |

@@

#4. Objective
#5. Summary of variables
##5.1 Individual variable summary

@@

#6. Relationship between variables
##6.1. NPT4_COMBINE VS State

@@

##6.2. Debt VS Cost
We assume there would be a strong linear relationship between the average net price for Title IV institutions and the median debt for students who have completed. We hypothese that the students who completed education in colleges with high costs will have a highe value of median debt. We use the following code to generate the scatterplot between these two variables to verify our assumptions.

@@

##6.3. Percentage of Pell Grant VS college type(CONTROL)

@@

##6.4  Percentage first-generation students VS Status
To compare the Percentage first-generation students with the different states, we grouped data into the state level to take a further analysis.

@@

##6.5 family income with Pell Grant
We assume there would be a strong linear relationship between family income and the percentage of students who can receive the Pell Grant. We hypothese that colleges with small value of family income would tend to have high percentages of Pell Grant. The following codes are used to generate the scatter pkot between these two varaibles.

@@

##6.6 cost and median debts with earning

@@

##6.7 default with earning

@@

##6.8 degree type vs. earning

@@

##6.9 predominant degree, control  and earning after 6 year of entry
The following plot shows two factor variables (predominant degree award variable and control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry. Our team uses the function geom_tile()[ggplot2 package] to visualize the correlation matrix.

@@

##6.10 predominant degree + control (count)
The following plot shows the relationship between two factor variables (predominant degree award variable and control variable). Our team uses the function geom_bar() to map the counting values to y, ctrF variable to x and the preF variable to the fill of the bar.

@@

Our team further uses the function xtabs() to calculate the exact number for each predominant degree awarded by different types of colleges.
```{R}
 data_clean %>%
 xtabs(formula = ~preF+ctrF)
```

 #6.11 control + earning
The following plot shows one factor variable (control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry). We use the 
geom_violin() using the default scale = “area” argument and geom_boxplot() function to explore the relationship. The plot superimposed with boxplots shows side-by-side violin plots of median earnings of students working and not enrolled 6 years after entry according to different college types.
